Adopting agile in the large: motivations, success factors and challenges

### 2013-11-27 journal/article.tex
Coding description

An integrated deductive and inductive approach was chosen for coding the primary
studies \cite{Cruzes2011a}. Initially a list of codes was established for the
contextual information, as presented in Table \ref{table:contextualcodes}. The
codes related to the research questions were chosen to be created by an
inductive procedure. The reason for inducting codes rather than using an a
priori approach was to avoid the researchers' previous assumptions of the
research area to affect the choice of codes. To give direction for choosing the
codes seven different code families were established (see Table
\ref{table:codefamilies}), including a description defining the scope of the
families and examples for codes. The example codes would not necessarily be used
as actual codes, and would not represent the entire or final scope of the
families.

@@

		Practices &
		Distinguishable practices that are used or established during transformation
		(coaching, piloting, continuous integration, communities of practice). Other
		distinguishable factors that are presented as neutral in the primary studies \\

		Other &
		Contextual codes, other codes not relating to RQ's. \\

>>>>

An integrated deductive and inductive approach was chosen for coding the primary
studies \cite{Cruzes2011a}. The coding was also designed to have a contextual
part and a findings part as suggested by Cruzes and Dybå \cite{Cruzes2011a}. A
list of codes was established for contextual information, as presented in Table
\ref{table:contextualcodes}. Codes related to the research questions were chosen
to be created by an inductive process. The reason for inducting codes rather
than using an a priori approach was to avoid the researchers' previous
assumptions of the research area to affect the choice of codes. To give
direction for code induction seven different code families were established (see
Table \ref{table:codefamilies}). A description defining scope and examples for
codes were defined for each family. The example codes would not necessarily be
used as actual codes, and would not represent the entire or final scope of the
families.

@@

		Practices &
		Distinguishable practices that are used or established during transformation.
		Factors that are presented as neutral in terms of successes and challenges
		in the primary studies.
		(coaching, piloting, continuous integration, communities of practice) \\

		Contextual &
		Contextual codes defined in Table \ref{table:contextualcodes}. \\
